### 2018-11-07 articleSFDS.tex
suppression comparaison DOE 100 et DOE50

This application section is developed in two subsections. The first subsection details the practical implementation procedure of the inference for each model. In the second subsection, we discuss all the results obtained for the models that we tried out.\newline

@@

To position the application case to a time consuming context, a limited number of experiments is allowed for the DOE which establishes the surrogate. We will limit the number of code calls to $50$ to investigate the time consuming situation and compare it to other situations more favorables. This number of experiments is taken when computer codes are extremely time consuming. To compare the quality of $\mathcal{M}_2$ with a DOE of $50$ points, we chose to compare it with a model $\mathcal{M}_2$ established with a DOE of $100$ points. \newline

\begin{table}[htbp!]
\centering
\caption{Results in cross validation for $\mathcal{M}_2$ for 2 different DOE sizes}
\label{tab:comparisonPG}
\begin{tabular}{c|c|c}

& $50$ points & $100$ points\\
\hline
\hline
coverage rate at 90\% (in \%) & 32 & 65 \\
\hline
RMSE of the instantaneous power ($W$) &21.61 &19.7 \\
\end{tabular}
\end{table}

The degradation in prediction with the decrease of the number of points in the DOE (Table \ref{tab:comparisonPG}) is in line with our desire to place ourselves in the most unfavorable case possible.

>>>>

This application section is developed in two subsections. The first subsection details the practical implementation procedures of the inference for each model. In the second subsection, we discuss all the results obtained for the models that we tried out.\newline

@@

To position the application case to a time consuming context, a limited number of experiments is allowed for the DOE which establishes the surrogate. We will limit the number of code calls to $50$ to investigate the time consuming situation and compare it to other situations more favorables. This number of experiments is taken when computer codes are extremely time consuming. \newline
%
% To compare the quality of $\mathcal{M}_2$ with a DOE of $50$ points, we chose to compare it with a model $\mathcal{M}_2$ established with a DOE of $100$ points. \newline
%
%\begin{table}[htbp!]
%\centering
%\caption{Results in cross validation for $\mathcal{M}_2$ for 2 different DOE sizes}
%\label{tab:comparisonPG}
%\begin{tabular}{c|c|c}
%
%& $50$ points & $100$ points\\
%\hline
%\hline
%coverage rate at 90\% (in \%) & 32 & 65 \\
%\hline
%RMSE of the instantaneous power ($W$) &21.61 &19.7 \\
%\end{tabular}
%\end{table}
%
%The degradation in prediction with the decrease of the number of points in the DOE (Table \ref{tab:comparisonPG}) is in line with our desire to place ourselves in the most unfavorable case possible.
